Adaptive Scheduling of Scientific Workflows

### 2024-03-07 main.tex
First three papers described. WIP for Section 3 Related Work

\documentclass[sigconf,review,anonymous]{acmart}
\usepackage{algorithmicx}
\usepackage{amsmath}
\usepackage{graphicx}
%\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{algpseudocode}
\usepackage{algorithm}

@@

@@

    Wang et al.~\cite{wang2019dynamic} proposes a dynamic particle swarm optimization algorithm to schedule workflows in a cloud.
    Particles are possible solution in the solution space.
    However, the dynamic is only in the choice of generation sizes, not in the changes in the execution environment.
    Singh et al.~\cite{singh2018novel} addresses dynamic provisioning of resources with a constraint deadline.
    However, the approach is for clouds.

@@

@@

            \For{$\nu_1, \nu_2 \in \Gamma \mid \nu_1 \in ( \Pi_{\nu_2} \cup C_{\nu_2})$} \label{line:neighbblocks}

            \State $\{\Gamma', \nu_m\} \gets $ \textsc{Merge}($\nu_1, \nu_2$); proc($\nu_m$)$\gets $ proc($\nu_1$);
            \State $\mu \gets $\textsc{Makespan}($\Gamma'$)
            \If{$r_{\nu_m} \leq M_{proc(\nu_m)}$ and $\mu \leq $ \textsc{Makespan}($\Gamma$)}
                \State $\Gamma \gets \Gamma'$
            \EndIf
            \EndFor

>>>>

\documentclass[sigconf,review,anonymous]{acmart}
\usepackage{algorithmicx}
\usepackage{amsmath}
%\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{xspace}

@@

\include{macros}

@@

    Wang et al.~\cite{wang2019dynamic} proposes a dynamic particle swarm optimization algorithm to schedule workflows in a cloud.
    Particles are possible solution in the solution space.
    However, the dynamic is only in the choice of generation sizes, not in the changes in the execution environment.
    Singh et al.~\cite{singh2018novel} addresses dynamic provisioning of resources with a constraint deadline.
    However, the approach is for clouds.
    \xspace

@@

    De Olivera~\etal~\cite{de2012provenance} propose a tri-criteria (makespan, reliability, cost) adaptive scheduling heuristic
    for clouds.
    Based on a 3-objective cost model, their greedy scheduling algorithm schedules tasks into machines.
    The authors use provenance data to make scheduling decisions.
    The cost model is a set of linear equations computed in the simulation environment, it represents the cost of an execution based on the criteria.
    In the algorithms, the authors test out 4 scenarios - one preferring each criteria, and a balanced one.
    The algorithm merely chooses the best virtual machine for each next task based on the cost given by the model.
    An additional algorithm combines several cloud activities (task executions) into one to improve the cost, so that each
    execution is not too small (utilize the granularity factor, the smallest entity of payment of the cloud producer).
    The authors used workflows with less than 10 tasks, but repeated them so that the execution had up to 200 tasks.
    They do not report the runtime of the scheduling algorithm, only the speedup and cost saving it produces.

    Rahman~\etal~\cite{rahman2013} propose a scheduling heuristic for grids that proposes mapping of tasks to machines by calculating
    the critical path in the graph dynamically at every step.
    They call it the dynamic critical path (DCP).
    For all tasks they compute the earliest start time and absolute latest start time that are upper and lower bounds
    on the start time of a task (differing by the slack this task has).
    All tasks on this critical path have the same earliest and latest start times, because they cannot be ddelayed.

    The algorithm takes the first unscheduled task on the critical path each time and maps it on a processor identified for it.
    If processors are heterogeneous, then the start times are computed with respect for the processor, and the minimum execution time for
    the task is chosen.
    The heuristic also uses the same processor to schedule parent and children tasks, as to avoid data transfer between processors.
    The authors evaluate their approaches on random workflows of the size up to 300 tasks.

    The authors provide an overview over (simpler) scheduling heuristics.
    For example, GRASP (generally randomized adaptive search procedure) conducts a number of iterations to search an optimal
    solution for mapping tasks on machines.
    A solution is generated at each step, and the best solution is kept at the end.
    The search terminates when a certain termination criterion is reached.
    It generates better results than other algorithms, because it explores the whole solution space.

    Avanes~\etal\cite{avanes2008adaptive} present a heuristic for networks in disaster scenarios.
    These networks are a set of DAG-shaped scenarios, out of which one needs to be executed.
    The scenario contains AND- and OR-branches, where AND-branches indicate acitivities that need to be executed in parallel.

    The heuristic first partitions the set into local schedules by using affinity matrices to determine similar
    activities and group them together.
    Then they physically allocate these partitions to groups of disaster responders and tasks within this group.
    They define a constraint system for that.
    The dynamic part deals with changes and distinguishes between retriable and compensation acitivities.
    The heuristic calculates a new execution path with these tasks.
    In general, this heuristic is not as related as it looks, because of very specific workflow and task structure.

@@

            \For{$\nu_1, \nu_2 \in \Gamma \mid \nu_1 \in ( \Pi_{\nu_2} \cup C_{\nu_2})$}
                \label{line:neighbblocks}
            \State $\{\Gamma', \nu_m\} \gets $ \textsc{Merge}($\nu_1, \nu_2$); proc($\nu_m$)$\gets $ proc($\nu_1$);
            \State $\mu \gets $\textsc{Makespan}($\Gamma'$)
            \If{$r_{\nu_m} \leq M_{proc(\nu_m)}$ and $\mu \leq $ \textsc{Makespan}($\Gamma$)}
                \State $\Gamma \gets \Gamma'$
            \EndIf
            \EndFor
